---
title: "Suitability"
author: "Anna Calle"
date: "11/8/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# Load required packages
library(rnaturalearthdata)
library(rnaturalearth)
library(sf)
library(raster)
```


Suitability 

- Depth: 25-100m
- Min sea surface temp: >22째C
- Max sea surface temp: <30째C
- Distance to shore: <25 nautical miles
- Current velocity: <1m/s
- Min dissolved oxygen: >4.41 mg/L (200.5 umol/L O2)

Defining variables
```{r}
min_depth <- -25 
max_depth <- -100
min_sst_value <- 22
max_sst_value <- 32
max_dist_shore <- 46300 #25 nautical miles converted to meters
max_cv_value <- 1
min_DO_value <- 200.5

```

Set-Up for Downloading Data Using the "Maricultura" Google Drive File Stream
```{r}
# Create a Root to Extract Files 
if(Sys.info()["sysname"] == "Windows"){ #If operating system is "Windows" use G: Drive
  team_path <- "G:/"
} else { # If it is not (i.e. Mac), use the Google Drive File Stream
  team_path <- "/Volumes/GoogleDrive/"
}

#Create the Full File Path
path <- paste0(team_path, "Shared drives/Bren GP 2020 maricultura/Data/Raw_Data/Active_Data_Layers")

```

Data for graphs
```{r}
# Read in Brazil's EEZ
eez_BRA <- read_sf(dsn = path,
                layer = "eez_BRA")
# Assign projection: SIRGAS 2000 / Brazil Polyconic
crs_BRA <- "+proj=poly +lat_0=0 +lon_0=-54 +x_0=5000000 +y_0=10000000 +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs"

# Brazil's outline in correct projection and cropped to the EEZ's extent
bound_BRA <- ne_countries(scale = 50, country = "Brazil", returnclass = "sf") %>%
  st_transform(crs_BRA) %>% 
  sf::st_crop( bound_BRA, y = extent(eez_BRA))


```



Reclassifying depth to have 1s only if it's in between 25-100m, and 0s otherwise
```{r}
# Read in file
depth_mask <- raster(paste0(path,"/depth_mask.tif"))

# Reclassification matrix for depth layer
rcl_mat_depth <- c(-Inf, max_depth, 0,
                   max_depth, min_depth, 1,
                   min_depth, Inf, 0)

# Reclassify the depth layer
depth_binary <- reclassify(depth_mask,rcl= rcl_mat_depth)

# Plot reclassified layer
plot(depth_binary)

```

Reclassify min SST layer to have 1s only if it is above 22째C, and 0s otherwise
```{r}
# Read in file
min_sst_mask <- raster(paste0(path,"/min_sst_mask.tif"))

# Reclassification matrix for min SST
rcl_matrix_min <- c( -Inf, min_sst_value, 0,
                min_sst_value, Inf, 1)

# Reclassify min SST
sst_binary_min <- reclassify(min_sst_mask, rcl = rcl_matrix_min)

# Plot reclassified layer
plot(sst_binary_min)

```

Reclassify max SST layer to have 1s only if it is less than 30째C, and 0s otherwise
```{r}
# Read in file
max_sst_mask <- raster(paste0(path,"/max_sst_mask.tif"))

# Reclassify matrix for max SST layer
rcl_matrix_max <- c( -Inf, max_sst_value, 1,
                max_sst_value, Inf, 0)

# Reclassify max SST layer
sst_binary_max <- reclassify(max_sst_mask, rcl = rcl_matrix_max)

# Plot reclassified layer
plot(sst_binary_max)

```

Reclassify max current velocity to have 1s only if it is less than 1m/s, and 0s otherwise
```{r}
# Read in file
max_cv_mask <- raster(paste0(path,"/max_cv_mask.tif"))

# Reclassification matrix for current layer
rcl_mat_current <- c(-Inf, max_cv_value, 1,
                   max_cv_value, Inf, 0)

# Reclassify the depth layer
current_binary <- reclassify(max_cv_mask ,rcl= rcl_mat_current)

# Plot reclassified layer
plot(current_binary)
```

Reclassify distance to shore layer to have 1s only if it is less than 25nm, and 0s otherwise
```{r}
# Read in file
dist_shore <- raster(paste0(path,"/dist_shore.tif"))

# Reclassify matrix for distance to shore layer
rcl_matrix_dist_shore <- c( -Inf, 0, 0,
                            0, max_dist_shore, 1,
                            max_dist_shore, Inf, 0)

# Reclassify distance to shore layer
dist_shore_binary <- reclassify(dist_shore, rcl = rcl_matrix_dist_shore)

# Plot reclassified layer
plot(dist_shore_binary)
```

Reclassify DO layer to have 1s only if it is above 200.5 umol, and 0s otherwise
```{r}

# Units? \xbemol/m\x9f mol/ m3
# Read in file
DO_min_mask <- raster(paste0(path,"/DO_min_mask.tif"))

# Reclassification matrix for DO
rcl_matrix_DO <- c( -Inf, min_DO_value, 0,
                min_DO_value, Inf, 1)

# Reclassify DO min
DO_min_binary <- reclassify(DO_min_mask, rcl = rcl_matrix_DO)

# Plot reclassified layer
plot(DO_min_binary)
```


Suitable areas
```{r}
# Overlay all layers
# Note: they all need to have the same extent and resolution
suitable <- overlay(sst_binary_min, sst_binary_max, depth_binary, current_binary, dist_shore_binary, fun = function(a, b, c, d, e){a*b*c*d*e})

# Plot suitable areas
plot(suitable)

```

```{r}
# Color palette
pal <- colorNumeric(c("#41B6C4", "#fc7303"), values(suitable), na.color = "transparent")

# Leaflet map
suitable_leaflet <- leaflet() %>% 
  addTiles() %>%
  addRasterImage(suitable, colors = pal)

suitable_leaflet

```

